Surface ozone is a secondary air pollutant produced during the atmospheric photochemical degradation of emitted volatile organic compounds (VOCs) in the presence of sunlight and nitrogen oxides (\ce{NO_x}). 
Temperature directly influences ozone production through speeding up the rates of chemical reactions and increasing the emissions of VOCs, such as isoprene, from vegetation.
In this study, we used an idealised box model to examine the non-linear relationship between ozone, \ce{NO_x} and temperature, and compared this to previous observational studies.
Under high-\ce{NO_x} conditions, an increase in ozone from $20$~\degree C to $40$~\degree C of up to $20$~ppbv was due to faster reaction rates while increased isoprene emissions added up to a further $11$~ppbv of ozone.
The increased oxidation rate of emitted VOC with temperature controlled the rate of \ce{O_x} production, the net influence of peroxy nitrates increased net \ce{O_x} production per molecule of emitted VOC oxidised.
The rate of increase in ozone mixing ratios with temperature from our box model simulations was about half the rate of increase in ozone with temperature observed over central Europe or simulated by a regional chemistry transport model.
Modifying the box model setup to approximate stagnant meteorological conditions increased the rate of increase of ozone with temperature as the accumulation of oxidants enhanced ozone production through the increased production of peroxy radicals from the secondary degradation of emitted VOCs.
The box model simulations approximating stagnant conditions and the maximal ozone production chemical regime reproduced the $2$~ppbv increase in ozone per \degree C from the observational and regional model data over central Europe.
The simulated ozone-temperature relationship was more sensitive to mixing than the choice of chemical mechanism.
Our analysis suggests that reductions in \ce{NO_x} emissions would be required to offset the additional ozone production due to an increase in temperature in the future.
