\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf, .png, .jpg}
\usepackage{style}

\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\sloppy

\title{The Influence of Temperature on Ozone Production under varying \ce{NO_x} Conditions -- a modelling study: Supplementary Material}
\author[1]{J. Coates}
\author[1]{K. Mar}
\author[2]{N. Ojha}
\author[1]{T. Butler}
\affil[1]{Institute for Advanced Sustainability Studies, Potsdam, Germany}
\affil[2]{Max Planck Institute for Chemistry, Mainz, Germany}

\renewcommand\Authands{ and }

\begin{document}

\maketitle

\section{Vertical Mixing with Diurnal Boundary Layer Height} 
The MECCA box model used in \citet{Coates:2015} included a constant boundary layer height of $1$~km and no interactions (vertical mixing) with the free troposphere.
In reality, the planetary boundary layer (PBL) height varies diurnally and affects chemistry by diluting emissions after sunrise when the PBL rises. 

The expansion of the PBL into the free troposphere introduces vertical mixing with those chemical species present in the free troposphere. 
When the PBL collapses in the evening, pollutants are trapped in the PBL.  
The mixing layer height was measured as part of the BAERLIN campaign \citep{Bonn:2016} over Berlin, Germany. 
The profile of mean mixing layer height during the campaign period (June -- August 2014) was used in the model to represent the diurnal cycle of the mixing layer height.

The concentrations of the chemical species within the PBL are diluted due to the larger mixing volume when the PBL height increases at the beginning of the day, also the increasing PBL height mixes the chemical species from the free troposphere with the chemical species within the PBL i.e. vertical mixing. 
The PBL height collapses during night leaving the stable nocturnal boundary layer, trapping the chemical species into a smaller volume thus increasing the concentrations of the chemical species.
This vertical mixing scheme was implemented into the boxmodel using the same approach of \citet{Lourens:2016}.

The mixing ratios of \ce{O3}, CO and \ce{CH4} in the free troposphere were respectively set to $50$~ppbv, $116$~ppbv and $1.8$~ppmv. 
These conditions were taken from the MATCH-MPIC chemical weather forecast model on the 21st March (the start date of the simulations). 
The model results (\url{http://cwf.iass-potsdam.de/}) at the 700 hPa height were chosen and the daily average was used as input into the boxmodel.

\section{Allocation of Benelux AVOC emissions to Mechanism Species}
Anthropogenic NMVOC emissions over Benelux specified by the TNO\_MACCIII emission inventory \citep{Kuenen:2014} were translated to MCM~v3.2 emissions (Table~\ref{t:Benelux_MCM_emissions}).
The MCM~v3.2 emissions for each initial species were translated to emissions of mechanism species from into CRI~v2, MOZART-4 and RADM2 chemical mechanisms by weighting with the carbon numbers (Tables~\ref{t:CRI_NMVOC_emissions} -- \ref{t:RADM2_NMVOC_emissions}).
The allocation of MCM~v3.2 emissions into CB05 species followed the recommendations of \citet{Yarwood:2005} (Table~\ref{t:CB05_NMVOC_emissions}).

{
    \begin{landscape}%
        \centering%
        \input{Benelux_MCM_emissions}
    \end{landscape}%
}
\newpage
{
    \centering%
    \input{table_CRI_NMVOC_emissions}
}
\newpage
{
    \centering%
    \input{table_MOZART_NMVOC_emissions}
}
\newpage
{
    \centering%
    \input{table_RADM2_NMVOC_emissions}
}
\newpage
%{
%    \begin{landscape}%
%        \centering%
%        \input{table_CB05_NMVOC_allocations}
%    \end{landscape}%
%}

{
    \centering%
    \input{table_CB05_NMVOC_emissions}
}

\onehalfspacing
\bibliographystyle{abbrvnat}
\bibliography{References} 

\end{document}
